\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{TLCresume}

%====================
% CONTACT INFORMATION
%====================
\def\name{RAVINDRA KANOJIYA}
\def\phone{+91-8840353656}
\def\city{Lucknow, Uttar Pradesh}
\def\email{ravi.kanojiya211@gmail.com}
\def\LinkedIn{ravindra-a55b28220}
\def\github{Ravindra8896}
\def\role{Data Analyst $\cdot$ Python $\cdot$ SQL $\cdot$ Power BI $\cdot$ Tableau  $\cdot$ Machine Learning $\cdot$ EDA $\cdot$ Excel}
\def\portfoliourl{https://github.com/Ravindra8896}
\def\portfolioname{GitHub Portfolio}

\input{_header}
\begin{document}\pagestyle{others}\thispagestyle{first_page}

%====================
% OBJECTIVE
%====================
\objective{
Results-driven BCA graduate and Data Science Specialist (upGrad) with hands-on expertise in Python, SQL, Power BI, and Machine Learning.
Proven ability to translate raw data into actionable business insights — from a 110K+ record healthcare EDA to a \rupee79M e-commerce sales dashboard.
Currently building expertise in predictive modeling, customer segmentation, and time-series forecasting.
Seeking a Data Analyst role to drive data-backed decision-making and measurable business impact.
}

%====================
% SKILLS
%====================
\section{Skills}
\begin{tabular}{p{11em} p{1em} p{43em}}
\skills{Languages}       & & Python (Pandas, NumPy, Seaborn, Matplotlib, Scikit-learn), SQL, C, C++ \\
\skills{Analytics Tools} & & Power BI (DAX, Measures), Tableau, Advanced Excel (Pivot Tables, VLOOKUP, Power Query), Google Sheets \\
\skills{Machine Learning} & & Linear Regression, Logistic Regression, Decision Tree, Random Forest, K-Means Clustering, KNN, SVM \\
\skills{Data Skills}     & & EDA, Feature Engineering, Data Cleaning, Statistics, Time-Series Analysis, Customer Segmentation \\
\skills{Visualization}   & & Interactive Dashboards, KPI Cards, Reporting Automation, Trend Analysis \\
\skills{Tools \& Platforms} & & Jupyter Notebook, VS Code, Google Colab, Git, GitHub \\
\end{tabular}

%====================
% EXPERIENCE
%====================
\section{Technical Experience}

\subsection{Service Excellence Specialist $|$ ADDA247 \hfill Dec 2025 -- Present}
\begin{itemize}
    \item Monitor and analyze NPS and ticket-trend dashboards to identify recurring operational bottlenecks, supporting faster resolution cycles across product teams.
    \item Execute data-driven quality audits for product launches, leveraging defect-pattern analysis to improve product reliability and reduce post-launch issues.
    \item Built automated reporting frameworks in Excel and Google Sheets, eliminating manual effort and enabling real-time cross-functional decision-making.
\end{itemize}

\subsection{Senior Exam Counselor $|$ ADDA247 \hfill Sept 2024 -- Aug 2025}
\begin{itemize}
    \item Leveraged structured database tracking and client interaction analysis to increase lead conversion by \textbf{15\%} within the first quarter.
    \item Applied data-backed counseling strategies to improve enrollment rates for JAIIB/CAIIB aspirants, aligning student profiles with program requirements.
    \item Recognized as \textbf{Top Performer} multiple times for consistently exceeding revenue and student engagement targets.
\end{itemize}

%====================
% EDUCATION
%====================
\section{Education}

\subsection{Advanced Certificate in Data Science $|$ upGrad \hfill Aug 2025 -- Present}
\begin{itemize}
    \item Specializing in end-to-end Data Analysis, Predictive Modeling, and Machine Learning using Python (Pandas, Seaborn, Scikit-learn), Advanced SQL, Power BI, and Tableau.
    \item Completed MS-Excel: Basic to Advanced module covering Pivot Tables, Power Query, and decision-making tools (Feb 2026).
\end{itemize}

\subsection{Bachelor of Computer Applications -- CGPA: 8.1 $|$ DSEU, Dwarka \hfill 2021 -- 2024}
\begin{itemize}
    \item Built a strong foundation in \textbf{C, C++, Python}, OOP, DSA, SQL, and Data Science; applied Python libraries (Pandas, NumPy, Matplotlib) to real-world data analytics projects.
    \item Developed analytical thinking and cross-platform development skills (Linux, Windows, macOS), laying the foundation for a career in data analysis and machine learning.
\end{itemize}

%====================
% PROJECTS
%====================
\subsection{Intermediate (PCM) -- 76\% $|$ B. K. Convent Inter College \hfill 2021}

\subsection{High School (Mathematics) -- 78\% $|$ B. K. Convent Inter College \hfill 2019}

\section{Projects}

\subsection{Amazon E-Commerce Sales Analysis $|$ SQL + Python + Power BI + ML}
\item \textit{Tools: Python, Pandas, Seaborn, Advanced SQL, Power BI (DAX), Linear Regression, Scikit-learn} \hfill \href{https://github.com/Ravindra8896/Ecommerce-Sales-Analysis-SQL.git}{GitHub}
\begin{itemize}
    \item Analyzed 128,974 Amazon sales records using Advanced SQL and Python to extract KPIs on revenue, delivery efficiency, and regional performance across 36 states.
    \item Engineered time-series features (lag\_1, lag\_2, lag\_7, 7-day rolling mean) and trained a Linear Regression model for daily revenue forecasting (MAE: \rupee73,853).
    \item Built a 5-KPI interactive Power BI dashboard (\rupee79M revenue, 129K orders) with dynamic Top Category card, moving average trend line, and drill-through filters by category, state, and date.
    \item Identified \textit{Set} as top category (\rupee39M, 49\% revenue share) and Maharashtra as highest-revenue state (\rupee13M), enabling targeted sales strategy recommendations.
\end{itemize}

\subsection{Medical Appointment No-Show Analysis $|$ Python + EDA}
\item \textit{Tools: Python, Pandas, NumPy, Matplotlib, Seaborn, Feature Engineering} \hfill \href{https://github.com/Ravindra8896}{GitHub}
\begin{itemize}
    \item Analyzed 110,527 patient appointment records across 81 neighbourhoods to uncover drivers of a 20.19\% no-show rate using end-to-end EDA.
    \item Engineered scheduling weekday features and age-group bins, revealing zero Sunday appointments and a significantly lower Saturday volume compared to weekdays.
    \item Surfaced a counterintuitive insight: patients who received SMS reminders had a \textbf{higher} no-show rate (27.6\%) than those who did not (16.7\%) -- flagged for further investigation.
    \item Identified 21,801 hypertension and 7,943 diabetes patients as high-risk segments; 65\% of all appointments were booked by female patients.
\end{itemize}

\subsection{Supermarket Sales Dashboard $|$ Excel}
\item \textit{Tools: Microsoft Excel, Pivot Tables, Slicers, KPI Cards, Power Query} \hfill \href{https://github.com/Ravindra8896}{GitHub}
\begin{itemize}
    \item Analyzed 1,000 supermarket transactions (\$322,966 revenue) across 3 branches using Pivot Tables, Slicers, and KPI Cards to surface business insights.
    \item Identified Food \& Beverages as top category (\$56,144 -- 17.4\% share) and January as peak month (\$116,291 -- 19.5\% above 3-month average).
    \item Discovered that E-wallet and Cash are near-equally preferred (345 vs 344 orders) and 56.5\% of customers are loyalty Members -- informing retention strategy.
\end{itemize}

\subsection{Customer Segmentation Analysis $|$ Python + ML}
\item \textit{Tools: Python, Pandas, Scikit-learn, K-Means, Seaborn, Matplotlib} \hfill \href{https://github.com/Ravindra8896}{GitHub}
\begin{itemize}
    \item Applied K-Means clustering on transactional data to segment customers into high-value and low-value groups; used the Elbow Method for optimal cluster selection and Seaborn scatter plots for visualization.
\end{itemize}

%====================
% CERTIFICATIONS
%====================
\section{Certifications}
\begin{itemize}
    \item \textbf{MS-Excel: Basic to Advanced} -- upGrad (Feb 2026)
    \item \textbf{SQL Certification} (Basic \& Intermediate) -- HackerRank
    \item \textbf{Generative AI Fundamentals} -- Google Cloud \& Simplilearn
\end{itemize}

\end{document}
